---
title: "HW6"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(viridis)
library(p8105.datasets)
library(modelr)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(100)
```

# Problem 1

## Load dataset

```{r}
birthweight = read_csv("data/birthweight.csv") %>% 
  mutate(
    babysex = factor(babysex),
    frace = factor(frace),
    malform = factor(malform),
    mrace = factor(mrace)
  ) %>% 
  select(-pnumlbw, -pnumsga)
```

We drop "pnumlbw" and "pnumsage" column because they only have "0" values and give no information to differentiate the children.

## Regression Model

It is reasonable that a baby's weight is related to the mother's health condition during pregancy. Therefore, I build a model to fit the baby's birthweight to all the variables related the mother during pregancy

```{r}
fit = lm(bwt ~ delwt + menarche + mheight + momage + mrace + smoken + wtgain, data = birthweight)
```


```{r}
birthweight_fit = modelr::add_residuals(birthweight, fit)
modelr::add_predictions(birthweight_fit, fit) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() + 
  geom_smooth()
```


## Cross validation comparion with two other models

```{r}
cv_df = crossv_mc(birthweight, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)) %>% 
  mutate(
    mother_mod = map(train, ~lm(bwt ~ delwt + menarche + mheight + momage + mrace + parity + ppbmi + ppwt + smoken + wtgain, data = .x)),
    main_mod = map(train,~lm(bwt ~ blength + gaweeks,data = .x)),
    three_mod = map(train,~lm(bwt ~ bhead + blength + babysex 
                              + bhead*blength + bhead*babysex + blength*babysex 
                              + bhead*blength*babysex, data = .x))
  ) %>% 
  mutate(
    rmse_mother = map2_dbl(mother_mod, test ,~rmse(model = .x,data = .y)),
    rmse_main = map2_dbl(main_mod, test ,~rmse(model = .x,data = .y)),
    rmse_three = map2_dbl(three_mod, test ,~rmse(model = .x,data = .y))
  )
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

From the violin plot, we can see that the model using mother's variables is not as optimal as the model using baby's variables. 

# Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
bootstrap = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results1 = map(models, broom::glance),
    results2 = map(models, broom::tidy)
  ) %>% 
  select(-strap, -models) %>% 
  unnest(results1) %>% 
  select(.id, r.squared, results2) %>% 
  unnest(results2) %>% 
  select(-std.error, -statistic, -p.value) %>% 
  mutate(term = recode(term, `(Intercept)` = "b0", tmin = "b1")) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  mutate(log_value = log(b0*b1))  
```

```{r}
bootstrap %>% 
  ggplot(aes(r.squared)) + 
  geom_density()
```

```{r}
bootstrap %>% 
  ggplot(aes(log_value)) + 
  geom_density()
```

We can see that both distributions after bootstrapping is almost normal.

```{r}
bootstrap_results = 
  bootstrap %>% 
  summarize(
    lower_rsqr = quantile(r.squared,0.025),
    upper_rsqr = quantile(r.squared,0.975),
    lower_log = quantile(log_value,0.025),
    upper_log = quantile(log_value,0.975)
  )

bootstrap_results
```

The 95% confidence interval for $\hat r^2$ is (`r bootstrap_results[,1]`, `r bootstrap_results[,2]`), and 95% confidence interval for $log(\hat\beta_0 * \hat\beta_1)$ is (`r bootstrap_results[,3]`, `r bootstrap_results[,4]`)

